Assignment II\\Neural Networks and Deep Learning

### 2015-05-08 MLCV/ex2/report/report.tex
add case for only 1 neuron modified

    Let $\delta_j^L$ be the error of $j^{th}$ output neuron, then:
    \begin{equation}
      \delta_j^L = \frac{\partial C(a^L)}{\partial z_j^L} = \frac{\partial C(a^L)}{\partial a_j^L} \frac{\partial a_j^L}{\partial z_j^L}
    \end{equation}

@@

    \begin{equation}
      \frac{\partial a_j^L}{\partial z_j^L} = \frac{\partial f(z^L)}{\partial z_j^L} = f'(z_j^L)
    \end{equation}

@@

>>>>

    Let $\delta_j^L$ be the error of $j^{th}$ output neuron, then:
    \begin{equation}
      \delta_j^L = \frac{\partial C(a^L)}{\partial z_j^L} = \frac{\partial C(a^L)}{\partial a_j^L} \frac{\partial a_j^L}{\partial z_j^L}
      \label{eq:error_L}
    \end{equation}

@@

    \begin{equation}
      \frac{\partial a_j^L}{\partial z_j^L} = \frac{\partial f(z^L)}{\partial z_j^L} = f'(z_j^L)
      \label{eq:activ_L}
    \end{equation}

@@

    If, on the other hand, only a single neuron in one of the layers has a different activation function, the errors for that layer have to be computed for one neuron at a time. Suppose that all neurons but the neuron $j$ in layer $l$ use the sigmoid function $\sigma$ and this one neuron uses the function $f$. If $l = L$ equation \ref{eq:error_L} holds. Equation \ref{eq:activ_L} changes, however, for all but the $j^{th}$ neuron and it reads:

    \begin{equation}
     \frac{\partial a_j^L}{\partial z_j^L} = \frac{\partial \sigma(z^L)}{\partial z_j^L} = \sigma'(z_j^L)
    \end{equation}

    If $l < L$, then the error for the odd neuron reads:

    \begin{equation}
      \delta_j^l = f'(z_j^L) \sum_i w_{i, j}^{l+1} \delta_i^{l+1}
    \end{equation}

    and for all the other neurons of that layer:

    \begin{equation}
      k \neq j: \;\; \delta_k^l = \sigma'(z_k^L) \sum_i w_{i, k}^{l+1} \delta_i^{l+1}
    \end{equation}

    The simplicity and symmetry of matrix-matrix multiplication is therefore lost and errors have to be computed element-wise. Again, the gradient equations do not change.
